The SMT Competition 2015--2018

### 2019-08-16 2018/report/SMT-COMP.tex
and -> while

\paragraph{Benchmarks with Unknown Status.}
Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
imitating existing solvers rather than truly innovating.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's \maintrack regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound e.g. on problems with known status) solvers.  Benchmarks with
disagreements are removed from the competition results.  This conservative approach was chosen over a voting system as this situation is expected to be rare as the SMT-LIB organisers go to a significant effort prior to each competition to update the statuses of problems. A manual investigation is therefore preferred over an automated resolution. Disagreements are reported to the solvers involved and in all cases have led to bugs in solvers being identified and fixed.
In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; and in 2018, there were no disagreements between
otherwise sound solvers.

>>>>

\paragraph{Benchmarks with Unknown Status.}
Another paradigm shift concerns the treatment of benchmarks with
unknown status.  Because of the difficulty to judge solver responses
for such benchmarks, SMT Competitions until 2015 only used benchmarks
whose status was known (i.e., that had been solved previously by
existing SMT solvers).  In 2015, 30,717 non-incremental benchmarks
from the SMT Library were not used for the competition because their
status was unknown.  However, this approach was criticized for
imitating existing solvers rather than truly innovating.  In~2016,
the SMT Library contained 29,724 non-incremental benchmarks with
unknown status; solver performance on these was evaluated but reported
separately.  Since 2017, all non-incremental benchmarks are eligible
for the competition's \maintrack regardless of status, and they
directly affect the competition results.  Solver responses for such
benchmarks are assumed to be correct, unless there is a disagreement
between two or more (otherwise sound e.g. on problems with known status) solvers.  Benchmarks with
disagreements are removed from the competition results.  This conservative approach was chosen over a voting system as this situation is expected to be rare as the SMT-LIB organisers go to a significant effort prior to each competition to update the statuses of problems. A manual investigation is therefore preferred over an automated resolution. Disagreements are reported to the solvers involved and in all cases have led to bugs in solvers being identified and fixed.
In 2016,
there were disagreements on 79 benchmarks; in 2017, only one benchmark
was removed; while in 2018, there were no disagreements between
otherwise sound solvers.
